Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-22 Papers/ms.tex
Caption

\section{Simulated Data}
To demonstrate the method, we generated a simulated dataset with a single
substructure. The image is shown in Figure~\ref{fig:simulated_image}, and
consists of 100 $\times$ 100 pixels. The PSF was compact and was
defined on a 5 $\times$ 5 grid. The data was created by firing only one ray
per pixel, and the inference was also carried out under the same level of
approximation. Since the model assumptions are all correct for this image, the
demonstration here is purely to illustrate the computational tractability of
the problem, and the kind of outputs we are capable of producing.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{simulated_image.pdf}
\caption{\label{fig:simulated_image}}
\end{center}
\end{figure}

>>>>

\section{Simulated Data}
To demonstrate the method, we generated a simulated dataset with a single
substructure. The image is shown in Figure~\ref{fig:simulated_image}, and
consists of 100 $\times$ 100 pixels. The PSF was compact and was
defined on a 5 $\times$ 5 grid. The data was created by firing only one ray
per pixel, and the inference was also carried out under the same level of
approximation. Since the model assumptions are all correct for this image, the
demonstration here is purely to illustrate the computational tractability of
the problem, and the kind of outputs the method can produce.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{simulated_image.pdf}
\caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
lens plus a single dark substructure. The image was blurred by a PSF and had
some noise added.\label{fig:simulated_image}}
\end{center}
\end{figure}
